Evolution of Processes in Delivering Reliable Software in the European Scientific Arena

### 2018-06-28 paper-ieee-trans.tex
fix refs

Major developments carried throughout the years were focused on providing new
functionalities, whereas in the early days the adoption of software engineering methodologies had a lower priority 
\cite{datagrid}. The released software was less tested, resulting in a higher rate of
rollbacks and patches applied to production systems, compared to the later projects. Thereby, the stability and
% Comment
%P1 C2 L18: Claiming that stability and reliability was regularly compromised is quite a bold statement -- it needs at least some citations, and preferably some explanation of what forms this compromise took for a few prominent cases.
reliability of the e--Infrastructures was often compromised \cite{lingrand-egee}, leading to outages
in the participant resource centers. Back in the days when Grid middleware was actively developed, researchers 
reported the need of improvements both in terms of reliability and performance \cite{campana-atlas}, eventually 
developing their own custom solutions \cite{kindermann}\cite{mendez-lorenzo} on top of the existing services.

@@

\bibitem{campana-atlas}
S. Campana  \emph{et al.},
``Analysis of the ATLAS Rome production experience on the LHC computing grid,''
\emph{IEEE First International Conference of e-Science and Grid Computing},
pp. 8-pp, 2005.

@@

\bibitem{mendez-lorenzo}
P. Mendez-Lorenzo, J. T. Moscicki and A. Ribon,
``Experiences in the gridification of the Geant4 toolkit in the WLCG/EGEE environment,''
\emph{IEEE Nuclear Science Symposium Conference Record},
vol. 2, 2006.

>>>>

Major developments carried throughout the years were focused on providing new
functionalities, whereas in the early days the adoption of software engineering methodologies had a lower priority. 
The released software was less tested, resulting in a higher rate of
rollbacks and patches applied to production systems, compared to the later projects. Thereby, the stability and
% Comment
%P1 C2 L18: Claiming that stability and reliability was regularly compromised is quite a bold statement -- it needs at least some citations, and preferably some explanation of what forms this compromise took for a few prominent cases.
reliability of the e--Infrastructures was often compromised \cite{lingrand-egee}, leading to outages
in the participant resource centers. Back in the days when Grid middleware was actively developed, researchers 
reported the need of improvements both in terms of reliability and performance \cite{campana-atlas}, eventually 
developing their own custom solutions \cite{kindermann}\cite{mendez-lorenzo} on top of the existing services.

@@

\bibitem{campana-atlas}
S. Campana  \emph{et al.},
``Analysis of the ATLAS Rome production experience on the LHC computing grid,''
\emph{IEEE 1st International Conference of e-Science and Grid Computing},
pp. 8-pp, 2005.

@@

\bibitem{mendez-lorenzo}
P. Mendez-Lorenzo, J. T. Moscicki and A. Ribon,
``Experiences in the gridification of the Geant4 toolkit in the WLCG/EGEE environment,''
\emph{IEEE Nucl. Sci. Symp. Conf. Rec.},
vol. 2, 2006.
